\section{Open-System Dynamics: Lindblad Master Equation with $\zeta$-Hex Mode Mixing}

To include dissipative and decoherence effects in the super-ray flux, we define a density operator $\rho(t)$ for the super-ray modes. 
The evolution obeys a generalized Lindblad master equation with mode-dependent $\zeta_{\hexagon}$ weighting:

\begin{equation}
\frac{d\rho}{dt} = -i [H_{\rm SR}(t) , \rho] 
+ \sum_{k,\ell} \gamma_{k\ell} \zeta_{\hexagon}(\omega_k,\omega_\ell) 
\Big( L_{k\ell} \rho L_{k\ell}^\dagger - \frac{1}{2}\{L_{k\ell}^\dagger L_{k\ell}, \rho\} \Big),
\end{equation}

where:

\begin{itemize}
\item $H_{\rm SR}(t) = \sum_k \omega_k \, a_k^\dagger a_k + \Phi_g(t)$ is the super-ray Hamiltonian including **time-dependent gravitational phase** $\Phi_g(t)$.
\item $L_{k\ell}$ are generalized jump operators mediating mode-to-mode transitions in the presence of PCR-induced asymmetry.
\item $\gamma_{k\ell}$ are decoherence rates, $\zeta_{\hexagon}(\omega_k,\omega_\ell)$ weights mode mixing according to the zeta-hex prescription.
\item $\{ \cdot , \cdot \}$ denotes the anticommutator.
\end{itemize}

This formulation allows controlled **interference, dissipation, and ergotropy concentration** across modes, bridging open quantum dynamics with the numerical FFT–SED implementation.

\subsection{Master Scalar ER=EPR Equation}

To capture entanglement-driven energy transport and holographic correlations, we define a scalar ER=EPR field $\Psi_{\rm ER}(t,x)$ representing modewise ergotropy amplitudes:

\begin{equation}
\frac{\partial \Psi_{\rm ER}}{\partial t} 
= -i \Big[ H_{\rm SR}(t) + \Phi_g(t) \Big] \Psi_{\rm ER} 
+ \sum_{k,\ell} \zeta_{\hexagon}(\omega_k,\omega_\ell)\, \mathcal{M}_{k\ell}\, \Psi_{\rm ER} 
- \frac{1}{2} \sum_{k,\ell} \Gamma_{k\ell} \Psi_{\rm ER},
\end{equation}

where:

\begin{itemize}
\item $\mathcal{M}_{k\ell}$ encodes mode-to-mode M-shift entanglement transfer, derived from $\langle a_k^\dagger a_\ell \rangle$ correlations.
\item $\Gamma_{k\ell}$ is the effective damping of each entangled pair.
\item The field $\Psi_{\rm ER}$ naturally encodes **ER=EPR correlations**: local ergotropy reflects nonlocal entanglement-mediated energy exchange.
\end{itemize}

\subsection{Numerical Correspondence}

\begin{tabular}{l l}
\textbf{Python / NumPy Function} & \textbf{Equation / Role} \\
\hline
\texttt{lindblad\_evolve(rho,H,Liouvillian)} & Lindblad master equation, Eq.~(40) \\
\texttt{zeta\_hex\_matrix(omega)} & Computes $\zeta_{\hexagon}(\omega_k,\omega_\ell)$ mixing, Eq.~(40--41) \\
\texttt{er\_epr\_evolve(Psi, H, M, Gamma)} & Master scalar ER=EPR equation, Eq.~(41) \\
\end{tabular}

\subsection{Time-Dependent Gravitational Phase}

The gravitational modulation is incorporated as a **phase driver**:
\begin{equation}
\Phi_g(t) = \int_0^t \phi_g(t')\, dt',
\end{equation}
where $\phi_g(t)$ can be extracted from the linearized metric or an external probe wave, consistent with the PCR-sourced asymmetric flux.

\subsection{Coupling to Super-Ray Flux}

Finally, the scalar ER=EPR field couples back to the flux tensor $\Phi_{\mu\nu}$ via:

\begin{equation}
\Phi_{\mu\nu} \to \Phi_{\mu\nu} + \alpha_{\rm ER} \, \Im \big[ (\partial_\mu \Psi_{\rm ER}) (\partial_\nu \Psi_{\rm ER})^\dagger \big],
\end{equation}

providing a **feedback channel from entanglement to classical ergotropy distribution** and linking quantum open-system dynamics to the macroscopic PCR+SED flux framework.