\documentclass[12pt]{article}
\usepackage{amsmath, amssymb, amsfonts, physics, graphicx, hyperref, color}

\title{Super-Rays: Unified PCR--SED Framework with $\tau$-clock, M-shift, and Geometric Phase Drivers}
\author{Travis Jones}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
We present a fully unified framework for \emph{super-rays}, ergotropic flux fields combining Post-Canonical Regauging (PCR) and UFT311 Stochastic Electrodynamics (SED). 
The formalism integrates $\tau$-clock reparametrization, oscillatory integral seeding, M-shift modulation, tetrahedral geometric scaffolding, Möbius spiral phase drivers, and zeta-hex weighted FFT filters. 
A Projective–Clifford Regauging operator $\mathcal{P}=\mathbf{1}+\varepsilon \Gamma(x)$ introduces an intrinsic antisymmetric component in the super-ray flux tensor $\Phi_{\mu\nu}$, producing torsion and parity-odd holographic effects. 
We provide both the Lagrangian formulation and its numerical Python correspondence, enabling visualization of ergotropy propagation, Möbius spiral evolution, and gravitational birefringence induced by PCR.
\end{abstract}

\section{Theoretical Framework}

\subsection{Spacetime and Super-Ray Fields}
Let spacetime coordinates be $x^\mu=(t,x,y,z)$ with metric $g_{\mu\nu}$ and covariant derivative $\nabla_\mu$. 
The scalar super-ray field $\psi(x)$ carries information; its PCR-regauged dynamics are governed by
\begin{equation}
\Phi_{\mu\nu} = \partial_\mu \psi_\nu - \partial_\nu \psi_\mu + \Gamma_{\mu\nu}(x),
\end{equation}
where $\Gamma_{\mu\nu}(x)$ encodes the PCR asymmetry.

\subsection{Unified Lagrangian}
The complete Lagrangian density reads:
\begin{align}
\mathcal{L} &= \frac{1}{2\kappa} R 
- (\nabla_\mu \psi^\dagger)(\nabla^\mu \psi) - V(|\psi|^2) \nonumber\\
&\quad - \frac{1}{4} \mathrm{Tr}(\mathcal{F}_{\mu\nu} \mathcal{F}^{\mu\nu}) 
- \lambda_1\,\bar\psi (\mathcal{P}^\dagger \gamma^\mu \nabla^\nu \mathcal{P}) \psi g_{\mu\alpha} g_{\nu\beta} m^{\alpha\beta} \nonumber\\
&\quad - \frac{\alpha}{2} \psi^\dagger (\Gamma_{[\mu}\nabla_{\nu]}\psi) \epsilon^{\mu\nu\rho\sigma} n_\rho u_\sigma + \mathrm{c.c.} 
- \frac{1}{2} \int d\omega\, \rho(\omega) |\tilde{\psi}(\omega)|^2 \zeta_{\hexagon}(\omega),
\end{align}
where the last term corresponds to zeta-hex weighted FFT SED filtering.

\subsection{Euler--Lagrange Equations}
\textbf{Scalar field:}
\begin{equation}
-\nabla^\mu\nabla_\mu\psi + V'(|\psi|^2)\psi 
- \beta\, \Gamma_{[\mu}\nabla_{\nu]}\psi\, S^{\mu\nu} = 0
\end{equation}

\textbf{PCR field (if dynamical):}
\begin{equation}
\nabla^\mu \mathcal{F}_{\mu\nu} + m_\Gamma^2 \Gamma_\nu = J_\nu^{\rm PCR}, 
\quad 
J_\nu^{\rm PCR} = \frac{\delta \mathcal{L}_{\rm int}}{\delta \Gamma^\nu}
\end{equation}

\textbf{Metric / Einstein equation:}
\begin{equation}
\frac{1}{\kappa} G_{\mu\nu} = \Phi_{(\mu\nu)} + \nabla^\alpha \Sigma_{\alpha\mu\nu} + T^{\rm matter}_{\mu\nu}
\end{equation}

\subsection{Flux Tensor Decomposition}
\begin{align}
\Phi_{\mu\nu} &= \Phi_{(\mu\nu)} + \Phi_{[\mu\nu]}, \\
\Phi_{(\mu\nu)} &= (\nabla_\mu\psi^\dagger)(\nabla_\nu\psi) + (\nabla_\nu\psi^\dagger)(\nabla_\mu\psi) - g_{\mu\nu}\,\mathcal{L}_{\rm SR}, \\
\Phi_{[\mu\nu]} &= \beta\,(\psi^\dagger \Gamma_{[\mu}\nabla_{\nu]}\psi + \mathrm{c.c.})
\end{align}

\subsection{Numerical / Python Correspondence}

\begin{tabular}{l l}
\textbf{Function} & \textbf{Equation / Role} \\
\hline
\texttt{tau\_map(t,Tc)} & $\tau$-clock reparametrization, Eq.~(5) \\
\texttt{S\_wave(x)} & Oscillatory integral seed, Eq.~(6) \\
\texttt{ema\_1d(y,alpha)} & EMA smoothing of $S$, Eq.~(7) \\
\texttt{m\_shift\_tau(...)} & M-shift modulation $m(\tau)$, Eq.~(8) \\
\texttt{tetra\_vertices(scale)} & Tetrahedral geometry vertices, Eq.~(9) \\
\texttt{tetra\_faces(V,m)} & Tetrahedral faces, Eq.~(9) \\
\texttt{mobius\_spiral\_trajectory(...)} & Möbius spiral $R(t)$, Eq.~(10--12) \\
\texttt{zeta\_hex\_example(omega)} & Zeta-hex FFT weighting, Sec.~3.6 \\
\texttt{sed\_filter\_time\_series(...)} & SED FFT filter, Eq.~(13) \\
\texttt{ergotropy\_proxy\_from\_buffer(...)} & Ergotropy diagnostic, Eq.~(14) \\
\end{tabular}

\subsection{Möbius Spiral Phase Driver}
\begin{align}
x(t) &= r \cos\theta \sin\phi \, m(\tau), \\
y(t) &= r \sin\theta \sin\phi \, m(\tau), \\
z(t) &= r \cos\phi \, m(\tau), \\
\theta &= \pi t, \quad \phi = n \theta / 2
\end{align}

\subsection{SED--FFT Filter}
\begin{equation}
\tilde{\psi}_{\rm filtered}(\omega) = \tilde{\psi}(\omega)\left[1 - \alpha_{\rm gain} \, \rho(\omega) \zeta_{\hexagon}(\omega)\right]
\end{equation}

\subsection{Ergotropy Proxy}
\begin{equation}
\mathcal{E}_{\rm proxy} = \sum_\ell \max\left(0, |\tilde{\psi}_\ell|^2 - S(\omega_\ell)\right)
\end{equation}

\section{Physical Consequences}
\begin{itemize}
\item Directional information transport via $\Phi_{[\mu\nu]}$ (non-reciprocal).
\item Gravitational birefringence: $h_L \neq h_R$ due to PCR coupling.
\item Torsion generation: $\Phi_{[\mu\nu]}$ sources $T^\alpha{}_{\mu\nu}$ affecting spin precession.
\item Holographic parity-odd currents: boundary operators $J_i^{\rm bdy}$.
\item Ergotropy concentration: super-ray modes carry localized usable energy.
\end{itemize}

\section{Appendix: Minimal Toy Model Lagrangian}
\begin{equation}
\mathcal{L} = \frac{1}{2\kappa} R 
- (\nabla_\mu \psi^\dagger)(\nabla^\mu \psi) 
- m^2|\psi|^2
+ \beta\, \psi^\dagger A_\mu \gamma^\mu \gamma^5 \psi
+ \alpha\, \psi^\dagger (A_{[\mu}\nabla_{\nu]}\psi) S^{\mu\nu}
\end{equation}

\section{References}
\bibliographystyle{plain}
\begin{thebibliography}{99}
\bibitem{dirichlet} Dirichlet, P.G.L., \emph{Lectures on Number Theory}, 1837.
\bibitem{sed} Boyer, T.H., Phys. Rev. D, 1975.
\bibitem{holo} Maldacena, J., Adv. Theor. Math. Phys., 1998.
\bibitem{pcr} [UFT94 PCR Regauging notes].
\bibitem{uft311} [UFT311 SED Vacuum Flux notes].
\end{thebibliography}

\end{document}